\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation (02/04/2025 to 04/02/2025).

\section{Team Meeting Attendance}


\begin{table}[H]
    \centering
    \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    \textbf{Total} & \textbf{3}\\
    Payton Chan & 3\\
    Eric Chen & 3\\
    Fondson Lu & 3\\
    Jason Tan & 3\\
    Angela Wang & 3\\
    \bottomrule
    \end{tabular}
\end{table}

Meeting records can be found
\href{https://github.com/PlutosCapstone/Plutos/issues?q=label%3Ameeting%20is%3Aclosed%20}{here}.

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
    \centering
    \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Meetings}\\
    \midrule
    \textbf{Total} & \textbf{0}\\
    Payton Chan & 0\\
    Eric Chen & 0\\
    Fondson Lu & 0\\
    Jason Tan & 0\\
    Angela Wang & 0\\
    \bottomrule
    \end{tabular}
    \end{table}
    
We do not have a supervisor for our project, and we have decided to switch our
usability testing Extra to a user manual.

\section{Lecture Attendance}

\begin{table}[H]
    \centering
    \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Lectures}\\
    \midrule
    \textbf{Total} & \textbf{1}\\
    Payton Chan & 1\\
    Eric Chen & 1\\
    Fondson Lu & 1\\
    Jason Tan & 1\\
    Angela Wang & 1\\
    \bottomrule
    \end{tabular}
\end{table}

Lecture: \href{https://github.com/PlutosCapstone/Plutos/issues/257}{Final Demo /
Documentation / EXPO, on March 7th, 2025.}

\section{TA Document Discussion Attendance}

\begin{table}[H]
    \centering
    \begin{tabular}{ll}
    \toprule
    \textbf{Student} & \textbf{Lectures}\\
    \midrule
    \textbf{Total} & \textbf{1}\\
    Payton Chan & 1\\
    Eric Chen & 1\\
    Fondson Lu & 1\\
    Jason Tan & 1\\
    Angela Wang & 1\\
    \bottomrule
    \end{tabular}
\end{table}

TA Discussion: \href{https://github.com/PlutosCapstone/Plutos/issues/284}{V\&V Report, on March 3rd, 2025}. 


\section{Commits}

\wss{For each team member how many commits to the main branch have been made
over the time period of interest.  The total is the total number of commits for
the entire team since the beginning of the term.  The percentage is the
percentage of the total commits made by each team member.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & Num & 100\% \\
Payton Chan &  & \%\\
Eric Chen &  & \%\\
Fondson Lu &  & \%\\
Jason Tan &  & \%\\
Angela Wang &  & \%\\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.  For
instance, if a team member has more commits to unmerged branches, these numbers
can be provided here.  If multiple people contribute to a commit, git allows for
multi-author commits.}

\section{Issue Tracker}

\wss{For each team member how many issues have they authored (including open and
closed issues (O+C)) and how many have they been assigned (only counting closed
issues (C only)) over the time period of interest.}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Payton Chan &  & \\
Eric Chen &  & \\
Fondson Lu &  & \\
Jason Tan &  & \\
Angela Wang &  & \\
\bottomrule
\end{tabular}
\end{table}

\wss{If needed, an explanation for the counts can be provided here.}

\wss{If your team has additional metrics of productivity, please feel free to
add them to this report.}

\end{document}